Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-12-07 Documents/Paper/ms.tex
Sentence about :) figure
Fixed mistake picked up by referee
DNest target distribution

Rather than working with a sequence of constrained prior distributions like in
Equation~\ref{eq:constrained_prior}, DNS
replaces the posterior distribution with an alternative target
distribution composed of a {\it mixture} of the prior distribution with the
constrained priors, facilitating mixing between the multiple modes
and along degeneracy curves.
This is similar to the idea of annealed importance sampling
\citep{neal} or parallel tempering \citep{pt},
where the target distribution is modified from the posterior to something
``easier''. However,
the sequence of distributions used in Nested Sampling avoids some of the
problems with annealing-based methods. In particular, there is no need to choose
a temperature schedule (a potentially large set of tuning parameters),
and the method does not fail when phase transitions
are present.
Figure~\ref{fig:challenges} shows a mock-up of a two dimensional posterior
density with three modes, one of which contains a strong dependence, and
another of which contains a phase transition.

@@

The ``dragging'' process works as follows, and must be carried out on
each component:
\begin{eqnarray}
u_i &:=& F(\xx_i; \hyperparams)\\
\xx_i' &:=& G(\xx_i; \hyperparams')
\end{eqnarray}
In other words, the components' parameters are transformed to $[0,1]$ using the
current value of the hyperparameters, and then transformed back using the
proposed value of the hyperparameters so they represent the new interim prior
rather than the old one.

>>>>

Rather than working with a sequence of constrained prior distributions like in
Equation~\ref{eq:constrained_prior}, DNS
replaces the posterior distribution with an alternative target
distribution composed of a {\it mixture} of the prior distribution with the
constrained priors, facilitating mixing between the multiple modes
and along degeneracy curves. The mixture of constrained priors is given by
a mixture of distributions like in Equation~\ref{eq:constrained_prior}:

\begin{eqnarray}
p(\theta) &=& \sum_{i=0}^n w_i
\frac{\pi(\theta)\mathds{1}\left[L(\theta) > l_i\right]}{X_i}
\end{eqnarray}
where $\{l_i\}$ is a set of likelihood thresholds or ``levels'',
constructed such that the associated prior mass $X_{i+1}$ of level
$i+1$ is approximately $e^{-1}$ times that of level $i$. The $\{w_i\}$ are a
set of mixture weights, usually chosen to emphasise the higher levels during
the initial stages of a run (while creating levels),
and set to uniform once the desired number of levels $n$ has been created.
See \citet{dnest}
for more details about DNS.

This is similar to the idea of annealed importance sampling
\citep{neal} or parallel tempering \citep{pt},
where the target distribution is modified from the posterior to something
``easier''. However,
the sequence of distributions used in Nested Sampling avoids some of the
problems with annealing-based methods. In particular, there is no need to choose
a temperature schedule (a potentially large set of tuning parameters),
and the method does not fail when phase transitions
are present.
Figure~\ref{fig:challenges} shows a mock two dimensional posterior
density with three modes, one of which contains a strong dependence, and
another of which contains a phase transition. The target distribution used by
DNS includes the prior as part of the mixture, so travel between the modes is
possible.

@@

The ``dragging'' process works as follows, and must be carried out on
each component:
\begin{eqnarray}
u_i &:=& F(\xx_i; \hyperparams)\\
\xx_i' &:=& G(u_i; \hyperparams')
\end{eqnarray}
In other words, the components' parameters are transformed to $[0,1]$ using the
current value of the hyperparameters, and then transformed back using the
proposed value of the hyperparameters so they represent the new interim prior
rather than the old one.
